%------------------------
% Resume - Maciej Łukasiewicz (English, tailored)
%------------------------

\documentclass[a4paper,20pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\hypersetup{hidelinks}
\usepackage{fancyhdr}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.530in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.45in}
\addtolength{\textheight}{1in}

\urlstyle{rm}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemWithoutTitle}[1]{
  \item\small{
    {\vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbullet~~\textbf{#1} & #2 \\
      \textit{#3} & \textit{#4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-3pt}}

\renewcommand{\labelitemi}{}
\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-----------------------------
%%%%%%  CV STARTS HERE  %%%%%%

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\LARGE Maciej Łukasiewicz}} & Email: \href{mailto:maciek.lukasiewicz61@gmail.com}{maciek.lukasiewicz61@gmail.com}\\
  \href{https://lukasiewicz.cc}{Portfolio: lukasiewicz.cc} & Phone:~~~+48-668-911-734 \\
  \href{https://github.com/citrustiara}{GitHub: ~~github.com/citrustiara} & \href{https://www.linkedin.com/in/maciej-lukasiewicz-85a264372}{LinkedIn: Maciej Łukasiewicz} \\
\end{tabular*}

%-----------EDUCATION-----------------
\section{~~Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Gdańsk University of Technology}{Gdańsk, Poland}
      {B.Eng. in Computer Science}{October 2023 -- present}
    \resumeSubheading{III Liceum Ogólnokształcące, Gdynia}{Gdynia, Poland}{Mathematics \& Computer Science (bilingual track)}{2019 -- 2023}
    \resumeSubHeadingListEnd

\vspace{-5pt}
\section{Skills}
	\resumeSubHeadingListStart
	\resumeSubItem{Programming Languages}{~~~~~Java, C++, Python, JavaScript, C, SQL, HTML/CSS}
	% \resumeSubItem{OOP \& Algorithms}{~~~~~Object-oriented design, data structures, Alpha-Beta Pruning, RPN expression evaluation}
	\resumeSubItem{AI / ML}{~~~~~AI model evaluation, prompt engineering, LLM output quality assessment (DataAnnotation)}
	\resumeSubItem{Databases}{~~~~~SQL (MySQL, T-SQL), ETL pipelines (SSIS), OLAP}
	\resumeSubItem{Frameworks \& Tools}{~~~~~Spring Framework, Angular, Node.js, ESP-IDF, Arduino, Git, Maven, Docker, LaTeX, Excel}
	\resumeSubItem{Platforms}{~~~~~Windows, Linux, ESP32}
	\resumeSubItem{Languages}{~~~~~~Polish (native), English (C2)}

\resumeSubHeadingListEnd
\vspace{-5pt}
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading{DataAnnotation}{Remote}
    {AI Evaluator}{2025 -- present}
    \resumeItemListStart
        \resumeItem{AI Model Evaluation}
          {Evaluated and improved responses generated by large language models; assessed reasoning, and factual accuracy.}
    \resumeItemListEnd
\vspace{0pt}
    \resumeSubheading{\href{https://worldchem.pl}{WorldChem Sp. z o.o.}}{Gdańsk, Poland}
    {Web Developer (Freelance)}{2025}
    \resumeItemListStart
        \resumeItem{Company Website}
          {Designed and deployed a modern, responsive website for a chemical raw materials supplier. Handled full setup: domain purchase, DNS configuration, domain email, hosting, and on-page SEO. HTML, CSS, JavaScript -- dynamic product search, RWD. {\href{https://worldchem.pl}{Worldchem.pl}}.}
    \resumeItemListEnd
\vspace{-2pt}
    \resumeSubheading{Mathematics \& CS Tutoring}{Tricity / Remote}
    {Private Tutor}{2023 -- present}
    \resumeItemListStart
        \resumeItem{Scope}
          {High-school level mathematics and computer science tutoring. IB HL Mathematics exam preparation.}
    \resumeItemListEnd
\vspace{-2pt}
    \resumeSubheading{Photography}{Tricity}
    {Freelance Photographer}{2021 -- present}
    \resumeItemListStart
        \resumeItem{Events}
          {Sports events, school proms, family parties, animals and portraits.}
    \resumeItemListEnd
\vspace{-2pt}
    \resumeSubheading{PC Building \& Servicing}{Tricity}
    {Freelance}{2021 -- present}
    \resumeItemListStart
        \resumeItem{Custom Builds}
          {Component selection and assembly of custom desktop computers.}
    \resumeItemListEnd

\resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\vspace{-5pt}
\section{Projects}
\resumeSubHeadingListStart
\resumeSubItem{Force Plate PRO (Python, ESP32, C++)}{Force plate platform for vertical jump analysis. Streams load-cell data at 1280 Hz to a Python desktop app; computes jump height, peak power, and velocity. Python, ESP32, C++, CS1238 ADC (2025)}
\vspace{2pt}
\resumeSubItem{Data Warehouse (SQL, SSIS, OLAP)}{University BI project -- data warehouse and ETL pipeline (SSIS) for analysing tram delays in Gdańsk. Star schema with SCD2, Python synthetic data generation, T-SQL stored procedures, MDX queries, OLAP cube. T-SQL, SQL Server, SSIS, Python (2025)}
\vspace{2pt}
\resumeSubItem{Backgammon (C++)}{Backgammon board game in C++ with a full OOP architecture and a player hierarchy (human player, AI). Demonstrates object-oriented design principles. C++, Visual Studio (2025)}
\vspace{2pt}
\resumeSubItem{Multi Connect Four (JavaScript)}{Connect 4 variant played simultaneously on four boards against an AI using the Alpha-Beta Pruning algorithm. JavaScript, HTML, CSS (2025)}
\vspace{2pt}
\resumeSubItem{RunCode -- Online Store (PrestaShop, Docker, Python)}{Team project replicating a real running gear store via web scraping; re-built in PrestaShop and deployed on a university cluster using Docker Compose. Python test suite, Google Analytics integration, and a professional Git workflow: feature branches, pull requests, and tracked issues throughout. PrestaShop, MySQL, Python, Docker (2025)}
\vspace{2pt}
\resumeSubItem{Infix to Postfix (C++)}{Command-line calculator converting infix expressions to Reverse Polish Notation (RPN) with step-by-step output. Implements a stack-based algorithm. C++ (2024)}
\resumeSubHeadingListEnd

\vspace{-5pt}
\section{Additional Information}
\begin{description}[font=$\bullet$]
\item {Interests: software development, embedded systems, sport}
\end{description}

\end{document}
